Predator clusters

### 2023-11-29 reports/01_predators.qmd
Clean up targets dependencies

library(sf)
library(targets)
library(terra)
library(tidyverse)

tar_load_everything(store = here::here("_targets"))
source(here::here("R", "sp.R"))
source(here::here("R", "predators.R"))
```

@@

The six most abundant species (in ind nmi\^-1).

@@

# Make "top six" predator sightings spatially aware
topsix_sf <- predators_agg %>% 
  semi_join(top_six, by = "species") %>% 
  left_join(select(top_six, species, common_name), by = "species") %>% 
  latlon_to_sf(coords = c("lon_mean", "lat_mean"))
# Create a template raster of the study area
effort_ext <- effort_sf %>% 
  st_transform(ant_proj()) %>% 
  ext()
rast_template <- rast(crs = as.character(ant_proj())[[1]],
                      extent = effort_ext,
                      resolution = 30e3)
# Rasterize effort by year
effort_rast <- effort_sf %>% 
  st_transform(ant_proj()) %>% 
  rasterize(rast_template,
            field = "nmi",
            by = "year",
            fun = sum)
# Rasterize the predator sightings by year and species
topsix_rast <- topsix_sf %>% 
  st_transform(ant_proj()) %>% 
  mutate(year_commonname = interaction(year, common_name)) %>% 
  rasterize(rast_template, 
            field = "count",
            by = "year_commonname",
            fun = sum)
# Normalize counts by effort
topsix_norm <- topsix_rast
for (i in seq(nlyr(topsix_rast))) {
  lyr_name <- names(topsix_rast)[i]
  lyr_year <- substr(lyr_name, 1, 4)
  effort_year <- effort_rast[lyr_year] %>% 
    subst(0, NA)
  topsix_norm[[i]] <- topsix_norm[[i]] / effort_year
}
# Average across years
topsix_climatology <- unique(top_six$common_name) %>% 
  map(function(sp) {
    sp_rast <- subset(topsix_norm, 
                      which(str_detect(names(topsix_norm), sp)))
    mean(sp_rast, na.rm = TRUE)
  }) %>% 
  set_names(unique(top_six$common_name)) %>% 
  rast()
# Classify raster (otherwise CRSE throw it all off)
topsix_clim_class <- topsix_climatology %>% 
  classify(rcl = c(0, 1, 5, 10, 50))

@@

# Make the map! 
ant_basemap() +
  tidyterra::geom_spatraster(data = topsix_clim_class) +
  geom_sf(data = tar_read("ant_sf", store = here::here("_targets"))) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = "Ind nmi^-1") +
  facet_wrap(~lyr) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top")

@@

ant_basemap(map_bbox) +
  tidyterra::geom_spatraster(data = effort_rast) +
  scale_fill_distiller(palette = "PuRd", 
                       direction = 1, 
                       na.value = NA) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -57, by = 2)) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  labs(fill = "nmi") +
  facet_wrap(~lyr) +
  expand_limits(fill = 0)

@@

topsix_class_df <- as.data.frame(topsix_class, xy = TRUE) %>% 
  pivot_longer(-c("x", "y"), 
               names_to = "name", 
               values_to = "count") %>% 
  separate_wider_delim(name, 
                       delim = ".", 
                       names = c("year", "species")) %>% 
  drop_na(count)

ant_basemap() +
  geom_raster(aes(x, y, fill = count), topsix_class_df) +
  geom_sf(data = tar_read("ant_sf", store = here::here("_targets"))) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = "Ind nmi^-1") +
  facet_grid(species ~ year) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "right",
        text = element_text(size = 8))
```

@@

soi_rast <- soi_sf %>% 
  st_transform(ant_proj()) %>% 
  mutate(year_species = interaction(year, species)) %>% 
  rasterize(rast_template, 
            field = "count",
            by = "year_species",
            fun = sum)

@@

soi_class_df <- as.data.frame(soi_class, xy = TRUE) %>% 
  pivot_longer(-c("x", "y"), 
               names_to = "name", 
               values_to = "count") %>% 
  separate_wider_delim(name, 
                       delim = ".", 
                       names = c("year", "species")) %>% 
  drop_na(count)

ant_basemap() +
  geom_raster(aes(x, y, fill = count), soi_class_df) +
  geom_sf(data = tar_read("ant_sf", store = here::here("_targets"))) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = "Ind nmi^-1") +
  facet_grid(species ~ year) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "right",
        text = element_text(size = 8))
```

@@

pred_rast <- pred_sf %>% 
  st_transform(ant_proj()) %>% 
  mutate(year_commonname = interaction(year, common_name)) %>% 
  rasterize(rast_template, 
            field = "count",
            by = "year_commonname",
            fun = sum)

@@

pred_class_df <- as.data.frame(pred_class, xy = TRUE) %>% 
  pivot_longer(-c("x", "y"), 
               names_to = "name", 
               values_to = "count") %>% 
  drop_na(count) %>% 
  mutate(name = map_chr(name, \(n) paste(strwrap(n, 20), collapse = "\n")))

@@

p <- ant_basemap() +
  geom_raster(aes(x, y, fill = count), bird_class_df) +
  geom_sf(data = ant_sf) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = "Ind nmi^-1") +
  facet_wrap(~ name, ncol = 5) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top",
        text = element_text(size = 8))

@@

p <- ant_basemap() +
  geom_raster(aes(x, y, fill = count), mammal_class_df) +
  geom_sf(data = ant_sf) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = "Ind nmi^-1") +
  facet_wrap(~ name, ncol = 3) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top",
        text = element_text(size = 8))

>>>>

library(sf)
library(targets)
library(terra)
library(tidyterra)
library(tidyverse)

tar_load(c("ant_sf", "effort_sf", "predators_agg"),
         store = here::here("_targets"))
source(here::here("R", "sp.R"))
source(here::here("R", "predators.R"))
```

@@

The six most abundant species (in ind km\^-1).

@@

# Make "top six" predator sightings spatially aware
topsix_sf <- predators_agg %>% 
  semi_join(top_six, by = "species") %>% 
  left_join(select(top_six, species, common_name), by = "species") %>% 
  latlon_to_sf(coords = c("lon_mean", "lat_mean"))
# Create a template raster of the study area
effort_ext <- effort_sf %>% 
  st_transform(ant_proj()) %>% 
  ext()
rast_template <- rast(crs = as.character(ant_proj())[[1]],
                      extent = effort_ext,
                      resolution = 30e3)
# Rasterize effort by year
effort_rast <- effort_sf %>% 
  st_transform(ant_proj()) %>% 
  rasterize_by("km", "year", sum, rast_template)

# Rasterize the predator sightings by year and species
topsix_rast <- topsix_sf %>% 
  st_transform(ant_proj()) %>% 
  mutate(year_commonname = as.character(interaction(year, common_name))) %>% 
  rasterize_by("count", "year_commonname", sum, rast_template)

# Normalize counts by effort
topsix_norm <- topsix_rast
for (i in seq(nlyr(topsix_rast))) {
  lyr_name <- names(topsix_rast)[i]
  lyr_year <- substr(lyr_name, 1, 4)
  effort_year <- effort_rast[lyr_year] %>% 
    subst(0, NA)
  topsix_norm[[i]] <- topsix_norm[[i]] / effort_year
}
# Average across years
topsix_climatology <- unique(top_six$common_name) %>% 
  map(function(sp) {
    sp_rast <- subset(topsix_norm, 
                      which(str_detect(names(topsix_norm), sp)))
    mean(sp_rast, na.rm = TRUE)
  }) %>% 
  set_names(unique(top_six$common_name)) %>% 
  rast()
# Classify raster (otherwise CRSE throw it all off)
topsix_clim_class <- topsix_climatology %>% 
  classify(rcl = c(0, 1, 5, 10, 50))

@@

# Make the map! 
ant_basemap() +
  geom_spatraster(data = topsix_clim_class) +
  geom_sf(data = ant_sf) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = expression("Ind km"^-1)) +
  facet_wrap(~lyr) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top")

@@

ant_basemap() +
  geom_spatraster(data = effort_rast) +
  scale_fill_distiller(palette = "PuRd", 
                       direction = 1, 
                       na.value = NA) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -57, by = 2)) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  labs(fill = "km") +
  facet_wrap(~lyr) +
  expand_limits(fill = 0)

@@

topsix_class_df <- topsix_class %>% 
  as.data.frame(xy = TRUE) %>% 
  pivot_longer(-c("x", "y"), 
               names_to = "name", 
               values_to = "count") %>% 
  separate_wider_delim(name, 
                       delim = ".", 
                       names = c("year", "species")) %>% 
  drop_na(count)

ant_basemap() +
  geom_raster(aes(x, y, fill = count), topsix_class_df) +
  geom_sf(data = tar_read("ant_sf", store = here::here("_targets"))) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = expression("Ind km"^-1)) +
  facet_grid(species ~ year) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "right",
        text = element_text(size = 8))
```

@@

soi_rast <- soi_sf %>% 
  st_transform(ant_proj()) %>% 
  mutate(year_species = as.character(interaction(year, species))) %>% 
  rasterize_by("count", "year_species", sum, rast_template)

@@

soi_class_df <- soi_class %>% 
  as.data.frame(xy = TRUE) %>% 
  pivot_longer(-c("x", "y"), 
               names_to = "name", 
               values_to = "count") %>% 
  separate_wider_delim(name, 
                       delim = ".", 
                       names = c("year", "species")) %>% 
  drop_na(count)

ant_basemap() +
  geom_raster(aes(x, y, fill = count), soi_class_df) +
  geom_sf(data = tar_read("ant_sf", store = here::here("_targets"))) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = expression("Ind km"^-1)) +
  facet_grid(species ~ year) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "right",
        text = element_text(size = 8))
```

@@

pred_rast <- pred_sf %>% 
  st_transform(ant_proj()) %>% 
  mutate(year_commonname = as.character(interaction(year, common_name))) %>% 
  rasterize_by("count", "year_commonname", sum, rast_template)

@@

pred_class_df <- as.data.frame(pred_class, xy = TRUE) %>% 
  pivot_longer(-c("x", "y"), 
               names_to = "name", 
               values_to = "count") %>% 
  drop_na(count) %>% 
  mutate(name = map_chr(name, \(n) paste(strwrap(n, 20), collapse = "\n"))) %>% 
  # one sighting each, maps not useful
  filter(!name %in% c("Antarctic prion", "Humpback whale"))

@@

p <- ant_basemap() +
  geom_raster(aes(x, y, fill = count), bird_class_df) +
  geom_sf(data = ant_sf) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = expression("Ind km"^-1)) +
  facet_wrap(~ name, ncol = 5) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top",
        text = element_text(size = 8))

@@

p <- ant_basemap() +
  geom_raster(aes(x, y, fill = count), mammal_class_df) +
  geom_sf(data = ant_sf) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = expression("Ind km"^-1)) +
  facet_wrap(~ name, ncol = 3) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top",
        text = element_text(size = 8))

### 2023-11-29 reports/02_stations.qmd
Clean up targets dependencies

ant_basemap(map_lim) +
  geom_sf(aes(color = time.of.day), zoop_sf, size = 0.2) +
  geom_sf(data = zoop_buffers_10k, color = "lightgrey", fill = NA) +
  geom_sf(data = zoop_buffers_15k, color = "lightgrey", fill = NA) +
  geom_sf(data = zoop_buffers_20k, color = "lightgrey", fill = NA) +
  facet_wrap(~ Year) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_color_manual(values = tod_pal()) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

@@

station_map <- function(var, pseudolog = FALSE) {
  zoop_trans <- zoop_sf
  if (pseudolog) {
    old_var <- var 
    var <- str_glue("log({var}+1)")
    zoop_trans[[var]] <- log(zoop_trans[[old_var]] + 1)
  }
  ant_basemap(map_lim) +
    geom_sf(aes(color = .data[[var]]), zoop_trans, size = 2, shape = 15) +
    facet_wrap(~ Year) +
    scale_x_continuous(breaks = c(-60, -55)) +
    scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
    { if (is.numeric(zoop_trans[[var]])) 
      scale_color_distiller(palette = "PuRd", direction = 1) } +
    coord_ant(map_lim) +
    theme(legend.position = "bottom")
}

>>>>

ant_basemap() +
  geom_sf(aes(color = time.of.day), zoop_sf, size = 0.2) +
  geom_sf(data = zoop_buffers_10k, color = "lightgrey", fill = NA) +
  geom_sf(data = zoop_buffers_15k, color = "lightgrey", fill = NA) +
  geom_sf(data = zoop_buffers_20k, color = "lightgrey", fill = NA) +
  facet_wrap(~ Year) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_color_manual(values = tod_pal()) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

@@

station_map <- function(var, pseudolog = FALSE) {
  zoop_trans <- zoop_sf
  if (pseudolog) {
    old_var <- var 
    var <- str_glue("log({var}+1)")
    zoop_trans[[var]] <- log(zoop_trans[[old_var]] + 1)
  }
  ant_basemap() +
    geom_sf(aes(color = .data[[var]]), zoop_trans, size = 2, shape = 15) +
    facet_wrap(~ Year) +
    scale_x_continuous(breaks = c(-60, -55)) +
    scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
    { if (is.numeric(zoop_trans[[var]])) 
      scale_color_distiller(palette = "PuRd", direction = 1) } +
    coord_ant(map_lim) +
    theme(legend.position = "bottom")
}

### 2023-11-29 reports/03_combined.qmd
Clean up targets dependencies

library(sf)
library(targets)
library(tidyverse)

tar_load_everything(store = here::here("_targets"))
source(here::here("R", "sp.R"))
source(here::here("R", "zoop.R"))
```

@@

@@

ant_basemap(map_lim) +
  stars::geom_stars(aes(fill = count), data = topfive_stars) +
  geom_sf(aes(color = time.of.day), zoop_sf, size = 0.2) +
  scale_x_continuous(breaks = c(-65, -60, -55)) +
  scale_y_continuous(breaks = c(-66, -64, -62, -60)) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      trans = scales::pseudo_log_trans(),
                      breaks = c(0, 25, 100, 400, 1000, 4000),
                      na.value = NA) +
  scale_color_manual(values = tod_pal()) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  coord_ant(map_lim) +
  facet_grid(species ~ year) +
  expand_limits(fill = 0) +
  theme(axis.text.x = element_text(size = 7),
        legend.position = "bottom",
        legend.title = element_blank())
```

@@

ant_basemap(map_lim) +
  stars::geom_stars(aes(fill = count), data = soi_stars) +
  geom_sf(aes(color = time.of.day), zoop_sf, size = 0.2) +
  scale_x_continuous(breaks = c(-65, -60, -55)) +
  scale_y_continuous(breaks = c(-66, -64, -62, -60)) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      trans = scales::pseudo_log_trans(),
                      breaks = c(0, 25, 100, 400, 1000, 4000),
                      na.value = NA) +
  scale_color_manual(values = tod_pal()) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  coord_ant(map_lim) +
  facet_grid(species ~ year) +
  expand_limits(fill = 0) +
  theme(axis.text.x = element_text(size = 7),
        legend.position = "bottom",
        legend.title = element_blank())
```

@@

ant_basemap(map_lim) +
  geom_sf(aes(color = ice_type), 
          ice_sf,
          size = 0.5) +
  scale_color_brewer("Ice category", palette = "YlGnBu") +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  facet_wrap(~ year) +
  theme(legend.position = "left")

>>>>

library(lubridate)
library(sf)
library(targets)
library(tidyverse)

tar_load(c("effort_sf", "predators_agg", "predators_stations", 
           "station_effort", "stations_ice", "zoop", "zoop_sf"),
         store = here::here("_targets"))
source(here::here("R", "sp.R"))
source(here::here("R", "zoop.R"))
```

@@

Visual description of line transect and point station aggregation, for supplemental.

```{r}
#| label: fig-aggregation
#| fig-cap: "Biophysical observations (e.g., macrozooplankton net tows and CTD casts) collected at stations (yellow point) were associated with visual surveys for predators collected along line transects. All visual surveys conducted within 15 km (shaded circle) and 3 days were aggregated with station observations to form sites. In this example, the station was sampled on August 15, 2016 and visual surveys were condected within 15 km of the station twice: on August 15 (red) and on August 23 (blue). Only the visual surveys collected on August 15 were associated with this site."
#| warning: false

points_to_line <- function(pts) {
  pts %>% 
    group_by(segmentid) %>% 
    summarize(begin = paste0(first(processID), first(interval)),
              end = paste0(last(processID), last(interval)),
              lbl = format(first(UTC_start), "%b %d %Y"),
              do_union = FALSE) %>% 
    mutate(segmentid = factor(segmentid, labels = lbl)) %>% 
    st_cast("LINESTRING")
}

tow_origin <- as.POSIXct("1899-12-31", tz = "UTC")
station_prj <- slice(zoop_sf, 25) %>% 
  st_transform(ant_proj()) %>% 
  mutate(tow.UTC = date.tow + (start.time.UTC - tow_origin),
         lbl = format(tow.UTC, "%b %d"))
station_buffer <- st_buffer(station_prj, 15e3)
station_bbox <- st_bbox(station_buffer) %>% 
  expand_bbox(1.5)
transect_prj <- effort_sf %>% 
  filter(between(UTC_start, 
                 station_prj$tow.UTC - days(3),
                 station_prj$tow.UTC + days(3))) %>% 
  st_transform(ant_proj()) %>% 
  st_intersection(station_buffer) %>% 
  mutate(lag = UTC_start - lag(UTC_start, default = UTC_start[1]),
         segmentid = factor(cumsum(lag > hours(6))))
transect_line <- transect_prj %>% 
  points_to_line()
transect_prj2 <- effort_sf %>% 
  filter(year == station_prj$Year) %>% 
  st_transform(ant_proj()) %>% 
  st_crop(station_bbox) %>% 
  mutate(lag = UTC_start - lag(UTC_start, default = UTC_start[1]),
         segmentid = factor(cumsum(lag > hours(6))))
transect_line2 <- transect_prj2 %>% 
  points_to_line()

transect_endpoints <- transect_prj2 %>% 
  filter(paste0(processID, interval) %in% c(transect_line2$begin, 
                                            transect_line2$end))

ant_basemap() +
  geom_sf(data = station_buffer,
          fill = "grey50",
          alpha = 0.1,
          linetype = "dashed") +
  geom_sf(aes(color = segmentid),
          transect_line2,
          linetype = "dotted",
          linewidth = 1) +
  geom_sf(aes(color = segmentid),
          transect_line,
          linewidth = 1) +
  geom_sf(data = station_prj,
          shape = 23,
          size = 4,
          fill = "gold") +
  scale_color_manual(values = c("firebrick", "cornflowerblue")) +
  coord_ant(station_bbox) +
  theme(legend.position = c(0.03, 0.98),
        legend.justification = c(0, 1),
        legend.title = element_blank())

@@

ant_basemap() +
  stars::geom_stars(aes(fill = count), data = topfive_stars) +
  geom_sf(aes(color = time.of.day), zoop_sf, size = 0.2) +
  scale_x_continuous(breaks = c(-65, -60, -55)) +
  scale_y_continuous(breaks = c(-66, -64, -62, -60)) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      trans = scales::pseudo_log_trans(),
                      breaks = c(0, 25, 100, 400, 1000, 4000),
                      na.value = NA) +
  scale_color_manual(values = tod_pal()) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  coord_ant(map_lim) +
  facet_grid(species ~ year) +
  expand_limits(fill = 0) +
  theme(axis.text.x = element_text(size = 7),
        legend.position = "bottom",
        legend.title = element_blank())
```

@@

ant_basemap() +
  stars::geom_stars(aes(fill = count), data = soi_stars) +
  geom_sf(aes(color = time.of.day), zoop_sf, size = 0.2) +
  scale_x_continuous(breaks = c(-65, -60, -55)) +
  scale_y_continuous(breaks = c(-66, -64, -62, -60)) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      trans = scales::pseudo_log_trans(),
                      breaks = c(0, 25, 100, 400, 1000, 4000),
                      na.value = NA) +
  scale_color_manual(values = tod_pal()) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  coord_ant(map_lim) +
  facet_grid(species ~ year) +
  expand_limits(fill = 0) +
  theme(axis.text.x = element_text(size = 7),
        legend.position = "bottom",
        legend.title = element_blank())
```

@@

ant_basemap() +
  geom_sf(aes(color = ice_type), 
          ice_sf,
          size = 0.5) +
  scale_color_brewer("Ice category", palette = "YlGnBu") +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  facet_wrap(~ year) +
  theme(legend.position = "left")

### 2023-11-29 reports/04_pred_clus.qmd
Clean up targets dependencies

tar_load_everything(store = here::here("_targets"))
source(here::here("R", "predators.R"))
source(here::here("R", "sp.R"))
source(here::here("R", "zoop.R"))
seaice_contours <- terra::unwrap(seaice_contours)
```

@@

ant_basemap(map_lim) +
  # Sea ice
  geom_tile(aes(x, y, fill = seaice_conc), 
            filter(seaice_conc_df, between(seaice_conc, 0.65, 1)),
            alpha = 0.8) +
  scale_fill_distiller(lim = c(0.65, 1),
                       palette = "Blues",
                       na.value = "transparent") +
  # Predator clusters
  ggnewscale::new_scale_fill() +
  geom_sf(aes(fill = pred_clust), 
          stations_clust, 
          size = 2, 
          shape = 22) +
  facet_wrap(~ Year) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_fill_brewer(palette = "Dark2") +
  guides(fill = guide_legend(override.aes = list(size = 3))) +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

@@

ant_basemap(map_lim) +
  # Predator clusters
  ggnewscale::new_scale_fill() +
  geom_sf(aes(color = pred_clust,
              linetype = contlabel), 
          cluster_kde, 
          fill = NA,
          linewidth = 1) +
  facet_wrap(~ pred_clust) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_color_brewer(palette = "Dark2") +
  scale_linetype_manual(values = c(2, 1), guide = "none") +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

>>>>

tar_load(c("nmds_df", "nmds_env", "nmds_envfit", "nmds_shepard", "nmds_sightings", 
           "nmds_stress", "predators_clust", "seaice_conc_df", "seaice_contours", 
           "sightings_clust", "sightings_cut", "sightings_gap", "sightings_indval", 
           "stations_clust", "zoop_sf"), 
         store = here::here("_targets"))
source(here::here("R", "predators.R"))
source(here::here("R", "sp.R"))
source(here::here("R", "zoop.R"))
seaice_contours <- terra::unwrap(seaice_contours)
```

@@

ant_basemap() +
  # Sea ice
  geom_tile(aes(x, y, fill = seaice_conc), 
            filter(seaice_conc_df, between(seaice_conc, 0.65, 1)),
            alpha = 0.8) +
  scale_fill_distiller(lim = c(0.65, 1),
                       palette = "Blues",
                       na.value = "transparent") +
  # Predator clusters
  ggnewscale::new_scale_fill() +
  geom_sf(aes(fill = pred_clust), 
          stations_clust, 
          size = 2, 
          shape = 22) +
  facet_wrap(~ Year) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_fill_brewer(palette = "Dark2") +
  guides(fill = guide_legend(override.aes = list(size = 3))) +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

@@

ant_basemap() +
  # Predator clusters
  ggnewscale::new_scale_fill() +
  geom_sf(aes(color = pred_clust,
              linetype = contlabel), 
          cluster_kde, 
          fill = NA,
          linewidth = 1) +
  facet_wrap(~ pred_clust) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_color_brewer(palette = "Dark2") +
  scale_linetype_manual(values = c(2, 1), guide = "none") +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```
